Q1 table

### 2021-12-23 Q1_table_characteristics_full.Rmd
hide APIs

#download data
# get the data directly from redcap:
# report #155 is Q1:
url <- "https://redcap.ispm.unibe.ch/api/"
token <- "F2725F15FE84D2832E2793BB23B0A62B"
formData <- list("token"=token,
                 content='report',
                 format='csv',
                 report_id='155',
                 csvDelimiter='',
                 rawOrLabel='raw',
                 rawOrLabelHeaders='raw',
                 exportCheckboxLabel='false',
                 returnFormat='csv'
)
response <- httr::POST(url, body = formData, encode = "form")
Q1_table <- httr::content(response)
#cut data at end of jan 31
published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
Q1_table <- Q1_table %>%
  filter(record_id <= 5296 | record_id %in% published_preprints)
Q1_table <- Q1_table %>%
  select(-contains("rob")) %>%
  select(-contains("risk_of_bias")) %>%
  select(-journal)

>>>>

#download data
# get the data directly from redcap:
# report #155 is Q1:
url <- "https://redcap.ispm.unibe.ch/api/"
token <- "################################"
formData <- list("token"=token,
                 content='report',
                 format='csv',
                 report_id='155',
                 csvDelimiter='',
                 rawOrLabel='raw',
                 rawOrLabelHeaders='raw',
                 exportCheckboxLabel='false',
                 returnFormat='csv'
)
response <- httr::POST(url, body = formData, encode = "form")
Q1_table <- httr::content(response)
#cut data at end of jan 31
published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
Q1_table <- Q1_table %>%
  filter(record_id <= 5296 | record_id %in% published_preprints)
Q1_table <- Q1_table %>%
  select(-contains("rob")) %>%
  select(-contains("risk_of_bias")) %>%
  select(-journal)
